---
title: "Liver Disease Prediction Report"
subtitle: "Generated with Liver Disease Predictions App"
author: "By Santiago Gonzalez Berruga"
date: '`r format(Sys.Date(),"%e de %B, %Y")`'
output:
  pdf_document:
    latex_engine: xelatex
    fig_caption: true
    
header-includes:
    - \usepackage{fancyhdr}
    
params:
  prediction: NA
  data_raw: !r NA
  data_pred: !r NA

---
<!-- QR image -->
\addtolength{\headheight}{1.0cm}
\pagestyle{fancyplain}
\rhead{\includegraphics[height=1.2cm]{Web_QR.png}}
\renewcommand{\headrulewidth}{0pt}


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NULL,
                      warning = FALSE, message = FALSE, 
                      fig.align="center")
```

```{r packages, include=FALSE}
# Load packages
library(knitr)
library(kableExtra)
library(ggplot2)
library(ggpubr)
library(dplyr)
library(rlang)
```

```{r script_plots, include=FALSE}
# Load script with plots functions
source("Script_Graficos_Report.R")
```


# Results:

The posible results of the prediction are *LD* (Liver disease patient) and *H* (Non liver disease patient).

The result* of the prediction with a 77% of precision is:  `r params$prediction`

\* Please note that these results are not a final diagnosis, but a support tool for specialists. The results have been generated with the \textcolor{blue}{\href{https://gonzalezberrugasantiago.shinyapps.io/Predict_Liver_Disease/}{Liver Disease Predictions web application}}


# Data:

The data provided to make the prediction are:

```{r echo=FALSE}
# Data table
params$data_raw %>%
kable(booktabs = TRUE,format = "latex",digits = 1,
longtable=TRUE) %>%
kable_styling(
latex_options = c("striped", "condensed","repeat_header"),
position = "center",
full_width = FALSE,
repeat_header_text = "Continuation",
repeat_header_continued="Continue on the next page")


```


\newpage

# Plots:

The following graphs show the data used to train the predictive model and overlap the data and results used in the prediction, allowing a better understanding of the results:


```{r pie_plots, echo=FALSE, fig.height=4, fig.width=8}
# Pie plots
p1 <- plot_gender(dataset = params$data_pred) # Gender
p2 <- plot_class(dataset = params$data_pred)  # Class
final_plot <- ggarrange(p1, p2, legend = "top")
final_plot
```





```{r hist_box_plots, echo=FALSE, fig.height=3.5, fig.width=8}
# Distplots and Boxplots

## Age
p1 <- plot_distplot(dataset = params$data_pred, var = Age, var_name = "Age") 
p2 <- plot_boxplot( dataset = params$data_pred, var = Age, var_name = "Age")
final_plot <- ggarrange(p1, p2, legend = "top")
final_plot

## TB
p1 <- plot_distplot(dataset = params$data_pred, var = TB, var_name = "TB")
p2 <- plot_boxplot( dataset = params$data_pred, var = TB, var_name = "TB")
final_plot <- ggarrange(p1, p2, legend = "top")
final_plot

## Alkphos
p1 <- plot_distplot(dataset = params$data_pred, var = Alkphos, var_name = "Alkphos")
p2 <- plot_boxplot( dataset = params$data_pred, var = Alkphos, var_name = "Alkphos")
final_plot <- ggarrange(p1, p2, legend = "top")
final_plot

## Sgpt
p1 <- plot_distplot(dataset = params$data_pred, var = Sgpt, var_name = "Sgpt")
p2 <- plot_boxplot( dataset = params$data_pred, var = Sgpt, var_name = "Sgpt")
final_plot <- ggarrange(p1, p2, legend = "top")
final_plot

## Sgot
p1 <- plot_distplot(dataset = params$data_pred, var = Sgot, var_name = "Sgot")
p2 <- plot_boxplot( dataset = params$data_pred, var = Sgot, var_name = "Sgot")
final_plot <- ggarrange(p1, p2, legend = "top")
final_plot

## TP
p1 <- plot_distplot(dataset = params$data_pred, var = TP, var_name = "TP")
p2 <- plot_boxplot( dataset = params$data_pred, var = TP, var_name = "TP")
final_plot <- ggarrange(p1, p2, legend = "top")
final_plot

## ALB
p1 <- plot_distplot(dataset = params$data_pred, var = ALB, var_name = "ALB")
p2 <- plot_boxplot( dataset = params$data_pred, var = ALB, var_name = "ALB")
final_plot <- ggarrange(p1, p2, legend = "top")
final_plot

## AG
p1 <- plot_distplot(dataset = params$data_pred, var = AG, var_name = "AG")
p2 <- plot_boxplot( dataset = params$data_pred, var = AG, var_name = "AG")
final_plot <- ggarrange(p1, p2, legend = "top")
final_plot

```
























